### 2019-03-21 paper/sex_selection_spacing-ver2.tex
First spell no longer covered

The share of urban women in the sample has fallen slightly over the
periods, even though India's population has become progressively more urbanized.
For the first and second periods, over 32\% of the women 
entering the first spell lived in urban areas, falling to 
30\% for the third period and 26\% in the last period.
The most likely explanation is that the age of marriage has increased
faster in urban areas than in rural areas.
Hence, there are relatively more urban women, but fewer show up in the
sample because they are not yet married.

@@

Age at marriage increased over time across all three education groups.
The most substantial increase was for women without any education, where
the average went from below 16 years of age to 18.5.
The smallest change is for the most educated women where the average age
at marriage went up by less than a year---from 19.6 to 20.4---across the 
four periods.

>>>>

The share of urban women in the sample has fallen slightly over the
periods, even though India's population has become progressively more urbanized.
The most likely explanation is that the age of marriage has increased
faster in urban areas than in rural areas.
Hence, there are relatively more urban women, but fewer show up in the
sample because they are not yet married.

@@

% Age at marriage increased over time across all three education groups.
% The most substantial increase was for women without any education, where
% the average went from below 16 years of age to 18.5.
% The smallest change is for the most educated women where the average age
% at marriage went up by less than a year---from 19.6 to 20.4---across the 
% four periods.
